\normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range}

### 2017-07-08 Manuscript.Rmd
Fixed size of title text

---
title: "Biometry of the invasive lionfish (*Pterois volitans*) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range"
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  pdf_document:
    fig_caption: yes
fontsize: 12pt
bibliography: references.bib
---

>>>>

---
title: \normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range}
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  pdf_document:
    fig_caption: yes
fontsize: 12pt
bibliography: references.bib
---
